Risk Perceptions for Wearable Devices

### 2015-03-06 tex-inputs/abstract.tex
Edited to clean up language

\begin{abstract}
Wearable devices bring great benefits but also new potential privacy and security risks that could expose users' activities without their awareness or consent.
Effective design of notifications and security controls for wearable devices will require careful attention to prevent habituation and treat user as a scarce resource, which requires understanding which risks have the potential to be most concerning to users.
In this paper, we conduct a large-scale survey to investigate user security and privacy concerns regarding wearable devices. We surveyed 1,784 Internet users for their perceptions of wearable devices and identify risks that are particularly concerning to users, measure the effect of data type and data recipient on perceived risk, study users' self-reported concerns, and compare wearable device risks to those of more familiar technologies.
We hope that this work will inform design of future privacy and security controls for wearable devices.
\end{abstract}

% A category with the (minimum) three required fields
\category{K.6.5.}{Management of Computing and Information Systems}{Security and protection}[Unauthorized access]

>>>>

\begin{abstract}
Wearable devices bring great benefits through their omnipresence and ability to capture new types of data. But they also create new privacy and security risks by potentially exposing users' activities without their awareness or consent. Effective design of notifications and security controls for wearable devices will require careful foresight to prevent habituation by treating user attention as a scarce resource, which requires understanding which risks have the potential to be most concerning to users. In this paper, we describe a large-scale survey that we conducted to investigate user security and privacy concerns regarding wearable devices. We surveyed 1,782 Internet users about their perceptions of wearable devices, in order to identify risks that are particularly concerning to users. We specifically controlled for the effects of data type and data recipient on the magnitude of perceived risks, while also collecting open-ended concerns. Finally, we compared wearable device risks to those of more familiar technologies. Our goal is for this work to inform the design of future privacy and security controls for wearable devices.
\end{abstract}

% A category with the (minimum) three required fields
%\category{K.6.5.}{Management of Computing and Information Systems}{Security and protection}[Unauthorized access]
